The Driving Forces of API Evolution

### 2015-05-25 thesis/paper.tex
API->apl pr int
review rel work elhamn

\newpage
\section{Introduction} \label{introduction}
%API Design background
As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}. The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. 
%Software Evolution background
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.

@@

Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws. The laws are presented in Table \ref{table:expl_laws}. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world. Two other types of systems are also identified; S-type systems and P-type systems. S-type systems are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. An example of a P-type system is a chess program. These types of programs can be derived from a specification, but the rules of the program have to be abstracted. In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible. Based on this, we consider APIs to be E-type systems, since they they are heavily dependant on the environment and its changes, and since it is not possible to create an exact specificaton of any considerably (!!!) large API.

>>>>

\newpage
\section{Introduction} \label{introduction}
%API Design background
As the software industry and the open-source movement continue to grow, the number of public Application Programming Interfaces (APIs) is steadily increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}. The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. 
%Software Evolution background
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.

@@

Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws. The laws are presented in Table \ref{table:expl_laws}. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world. Two other types of systems are also identified; S-type systems and P-type systems. S-type systems are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. An example of a P-type system is a chess program. These types of programs can be derived from a specification, but the rules of the program have to be abstracted. In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible. Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes. It is therefore not possible to create an exact specificaton of any non-trivial API.
